Thesis Title

### 2022-05-16 chapters/discussion.tex
Updates from Overleaf

Second generation sequencing so far represent the most popular technology applied in metagenomics \citep{rossen_practical_2018, loman_twenty_2015, loman_high-throughput_2012}. Second-generation methods require library preparation and an enrichment or amplification step \citep{hagemann_overview_2015}, a time-consuming, bias inducing procedure that is propagated to the resulting sequencing data. Another limitation is the size of the outputted sequences that, despite the massive throughput of some of the machines available, requiring a very small \ac{DNA} input load to produce up to billions of sequences \citep{loman_twenty_2015}, ranges from from 45 to 300 bases in length \citep{loman_performance_2012}. This is simply not enough to not only transverse the most repetitive genomic regions, and severely limits the sensitivity of the methodology. Additionally, the sequencing library comprises both nucleic acids from the patient and pathogens, therefore the sequence coverage of the potential pathogen depends on the ratio of host/pathogen nucleic acid present in the sample

>>>>

Second generation sequencing so far represent the most popular technology applied in metagenomics \citep{rossen_practical_2018, loman_twenty_2015, loman_high-throughput_2012}. Second-generation methods require library preparation and an enrichment or amplification step \citep{hagemann_overview_2015}, a time-consuming, bias inducing procedure that is propagated to the resulting sequencing data. Another limitation is the size of the outputted sequences that, despite the massive throughput of some of the machines available, requiring a very small \ac{DNA} input load to produce up to billions of sequences \citep{loman_twenty_2015}, ranges from from 45 to 300 bases in length \citep{loman_performance_2012}. This is simply not enough to not only transverse the most repetitive genomic regions, and severely limits the sensitivity of the methodology. Additionally, turnaround times range from several hours to a full days, not ideal for a timely diagnosis.

The presence of an overwhelming amount of host \ac{DNA} or \ac{RNA} is one of the most important problems to be addressed in \ac{SMg}.

The unbiased nature of \ac{SMg} allows the sequencing of the nucleic acid of all pathogens (including commensal microbes) and the host. However, this unbiased nature of SMg might lower the sensitivity of pathogen detection. As the sequencing library comprises both nucleic acids from the patient and pathogens, the sequence coverage of the pathogen depends on the ratio of host/pathogen nucleic acid present in the sample.

Long-reads also have the advantage of resolving structural variations and variants in repetitive regions, which are poorly resolved by short-reads and are often excluded in bioinformatics analysis.
